---
title: "Module 4 - Contingency Tables 1"
author: "Rushabh Barbhaya"
date: "December 5, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Analysis
1. Table 1 has a χ2 value of **0.7419** and **Hired/Not Hired** not significant.
2. The Odds Ratio for Table 1 tells us that **Females have < 50% odds of getting hired as compared to Males**.

# Tables and Figures
```{r dataIn, include=FALSE, echo=FALSE}
library(dplyr)
library(knitr)
library(kableExtra)

data <- read.csv("data.csv")
data = data.frame(data)
data$new[data$Hired == "Y"] <- "Hired"
data$new[data$Hired == "N"] <- "Not Hired"
specify_decimal <- function(x, k) trimws(format(round(x, k), nsmall=k))
```

```{r table, echo=FALSE, include=FALSE}
tabledata = data %>%  
  group_by(Gender) %>% 
  summarise("Hired" = sum(new == "Hired"), 
            "Not Hired" = sum(new == "Not Hired"),
            "Total" = n())
tabledata = tabledata %>% 
  mutate("% Hired" = as.numeric(specify_decimal((tabledata$Hired/tabledata$Total)*100, 2)),
         "Odds(Hired)" = as.numeric(specify_decimal((tabledata$Hired/tabledata$`Not Hired`), 2))) %>%
  arrange(desc(tabledata$Total))

tabledata
```

```{r output, echo=FALSE}
kbl(tabledata, caption = "Company wide hiring") %>% 
  kable_styling()
```

