---
title: "Module 3 - Fitting Discrete Distributions 2"
author: "Rushabh Barbhaya"
date: "December 12, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Analysis
```{r include=FALSE, echo=FALSE}
library(dplyr)
library(tidyr)
library(kableExtra)
library(vcd)

data = read.csv("data2.csv")

data$rSum = rowSums(data[,0:8] == 1)+rowSums(data[,0:8] == 2)+rowSums(data[,0:8] == 3)
tab = data %>%
  group_by(rSum) %>% 
  summarise(Successes = n()) %>% 
  spread(key = rSum, value = Successes) %>% 
  mutate(" " = "Successes", .before = 1) %>% 
  mutate("8" = 1-1)

dice_fit = goodfit(data$rSum, type = "binomial", par = list(size=8))
```
Perform a goodness-of-fit test.

1. The test’s statistic has a value of $χ^2$ = *6.897925* \n
2. The test has a p-value of *0.3303904* \n
3. The test provides evidence that *test result is not significant* because *p-value is not less than 0.05* \n

# Tables and Figures

Find the maximum dice size: `r max(data)`

Find the group size: `r length(unique(data$rSum))`

Considering a roll 1/2/3 to be a success, find the number of successes per group

```{r echo=FALSE}
kbl(tab, caption = "Number of successes when rolling a 12 sided dice.") %>%
  kable_styling()

plot(dice_fit, scale = "raw", type = "standing", shade = T, main = "Number of successes when rolling a 12 sided dice." ,xlab = "Number of Successes", ylab = "Counts")
```
```{r echo=FALSE, include=FALSE}
summary(dice_fit)
```

