---
title: "Assignment 2"
author: "Rushabh Barbhaya"
date: "November 15, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r include=FALSE}
data <- read.csv('data.csv', header = T, sep = ",", row.names = NULL)
library(knitr)
library(plyr)
library(dplyr)
library(tidyr)
library(magrittr)
library(kableExtra)
```


# Analysis

In the 2^nd^ and 3^rd^ tables:

  1.  The restaurants were displayed in the **order** they were because *they were arranged in decending order of overall stars.*
  2.  The **overall** column represents *average of stars.* 
  3.  The overall column was added to the table in the **position** it was because *it was merged with other table in that order.*
  4.  The sex/race columns were **grouped** together because *the are of the same category.* 

# Tables and Figures

Find the total number of cases: `r nrow(data)`

For each restaurant, find the total number of customers.

```{r, echo=FALSE}
df = data.frame(table(data$restaurant))
df = df[order(-df$Freq),]
df2 = as.numeric(format(round((df$Freq*100/nrow(data)),2), nsmall = 2))
df2 = cbind(df, df2)
#df2
df2 = rename(df2, c("Restaurant"="Var1", "Count"="Freq", "Percentage"="df2"))
row.names(df2) = NULL
kbl(df2, caption = "Restaurant customers") %>% 
  kable_styling()
  
# knitr::kable(df2, row.names = FALSE, caption = "Restaurant customers")
```

For each restaurent with **Sex.**

```{r complex, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
df3 = data %>%
  group_by(restaurant, sex) %>% 
  summarise(rating = as.numeric(format(round(mean(stars),2), nsmall = 2))) 
df3 = pivot_wider(df3, names_from = sex, values_from = rating)
# df3
df4 = data %>%
  group_by(restaurant) %>% 
  summarise(rating = as.numeric(format(round(mean(stars),2), nsmall = 2))) 
# df4
df5 = merge(df4, df3, by = "restaurant", all.x = T)
df5 = df5[order(-df5$rating),]
row.names(df5) = NULL

# df5
kbl(df5, caption = "Average Customer Rating by **Sex**", col.names = c("Restaurant", "Overall", "Female", "Male")) %>% 
  kable_styling() %>% 
  add_header_above(c(" "=2,"Sex"=2))
```
 
For each restaurant, find the average star rating by **Race.**

```{r complex2, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
df6 = data %>%
  group_by(restaurant, race) %>% 
  summarise(rating = as.numeric(format(round(mean(stars),2), nsmall = 2))) 
df6 = pivot_wider(df6, names_from = race, values_from = rating)
# df6
df7 = data %>%
  group_by(restaurant) %>% 
  summarise(rating = as.numeric(format(round(mean(stars),2), nsmall = 2))) 
# df7
df8 = merge(df7, df6, by = "restaurant", all.x = T)
df8 = df8[order(-df8$rating),]
row.names(df8) = NULL
# df8
kbl(df8, caption = "Average Customer Rating by **Race**", col.names = c("Restaurant", "Overall", "Black", "Hispanic", "Other", "White")) %>%
  kable_styling() %>%
  add_header_above(c(" "=2,"Race"=4))
```