---
title: "Module 6 - Logistic Regression 1"
author: "Rushabh Barbhaya"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r dataprep, include=FALSE, echo=FALSE, warning=FALSE}
library(ggplot2)
library(lmtest)

data = read.csv('data.csv')
names(data)[3] = 'Height'
names(data)[4] = 'Weight'
data$Improved = as.numeric(data$Improved)
fit1 = glm(Improved ~ Height, data = data, family = 'binomial')
fit2 = glm(Improved ~ Weight, data = data, family = 'binomial')
sum_fit_1 = summary(fit1)
sum_fit_2 = summary(fit2)

gg = ggplot(data, aes(x = Height, y = Improved)) + 
  theme_bw() +
  geom_point(position = position_jitter(height = 0.02, width = 0)) +
  stat_smooth(
    method = 'glm',
    method.args = list(family = 'binomial'),
    alpha = 0.1,
    fill = 'blue',
    size = 2.5,
    fullrange = T
  )

gg2 = ggplot(data, aes(x = Weight, y = Improved)) + 
  theme_bw() +
  geom_point(position = position_jitter(height = 0.02, width = 0)) +
  stat_smooth(
    method = 'glm',
    method.args = list(family = 'binomial'),
    alpha = 0.1,
    fill = 'blue',
    size = 2.5,
    fullrange = T
  )
```


# Analysis
1. `Height` [is not] a significant predictor of `Improved` ($\beta =$ `r exp(coef(fit1))['Height']`, p = `r sum_fit_1$coefficients[2,4]`).
2. For each cm in `Height`, the Odds of the subject’s symptoms [improve] by `r round((exp(coef(fit1))['Height']-1)*100,2)` %.
3. `Weight` [is] a significant predictor of `Improved` ($\beta =$ `r exp(coef(fit2))['Weight']`, p = `r sum_fit_2$coefficients[2,4]`).
4. For each kg in `Weight`, the Odds of the subject’s symptoms [improve] by `r round((exp(coef(fit2))['Weight']-1)*100,2)` %.

# Tables and Figures
```{r graphs, echo=FALSE, message=FALSE}
gg
gg2
```

